This page and the next page should be removed

### 2021-01-07 analysis/master_thesis.Rmd
proofread + apa7 figure captions

csl               : "manuscript_files/apa.csl"
documentclass     : "apa7"
classoption       : "doc,12pt,twoside"
mainfont          : "Times New Roman"
output:
  papaja::apa6_pdf:
    latex_engine:   "xelatex"

header-includes:
  - \setcounter{tocdepth}{2}
  - \raggedbottom
  - \linespread{1.5}
  - \geometry{a4paper,margin=25mm}
  - \fancyhead{}
  - \fancyheadoffset[RO,LE]{0pt}
  - \fancyhead[RO,LE]{\thepage}
  - \fancyhead[LO,RE]{Semantic Knowledge and Unfamiliar Objects}
  # - \addtolength\oddsidemargin {0.5cm}
  # - \addtolength\evensidemargin {-0.5cm}
  - \usepackage{setspace}
  - \AtBeginEnvironment{tabular}{\doublespacing}
  # - \AtBeginEnvironment{lltable}{\doublespacing}
  # - \AtBeginEnvironment{tablenotes}{\doublespacing}
  # - \captionsetup[table]{font={stretch=1.5}}
  - \captionsetup[figure]{font={stretch=1,scriptsize}}
  - \usepackage[all]{nowidow}
  - \usepackage[bottom]{footmisc}
  - \interfootnotelinepenalty=10000
  - \usepackage[export]{adjustbox}
---

@@

<!-- Title page -->
\thispagestyle{empty}
\begin{center}
\vspace*{10mm}
\textbf{Event-Related Potentials of the Semantically Informed}\\
\textbf{Perception of Unfamiliar Objects}\\
\vspace*{5mm}
\begin{figure}[h]
\begin{center}
\includegraphics[width=!,totalheight=!,scale=0.25]{master_thesis_files/hu_logo}
\end{center}
\end{figure}
{\setstretch{1.5}
Masterarbeit\\
an der\\
Humboldt-Universität zu Berlin\\
zur Erlangung des akademischen Grades \\
Master of Science (M.Sc.)\\
im Fach Psychologie\\
\vspace*{25mm}
}
\end{center}
\begin{flushleft}
{\setstretch{1.5}
\begin{tabular}{ll}
Vorgelegt von:&\textbf{Alexander Enge}\\
&geb. am 09.11.1996 in Räckelwitz\\
&Matrikelnummer 581331\\
Unter Betreuung von:&Prof. Dr. Rasha Abdel Rahman (Humboldt-Universität zu Berlin)\\
&Prof. Dr. Franziska Süß (Fachhochschule des Mittelstands)\\
&\\
Berlin, den 21.01.2021&\\
\end{tabular}
}
\end{flushleft}

@@

Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat, sed diam voluptua. At vero eos et accusam et justo duo dolores et ea rebum. Stet clita kasd gubergren, no sea takimata sanctus est Lorem ipsum dolor sit amet. Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat, sed diam voluptua. At vero eos et accusam et justo duo dolores et ea rebum. Stet clita kasd gubergren, no sea takimata sanctus est Lorem ipsum dolor sit amet. Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor danke frederik invidunt ut labore et dolore magna aliquyam erat, sed diam voluptua. At vero eos et accusam et justo duo dolores et ea rebum. Stet clita kasd gubergren, no sea takimata sanctus est Lorem ipsum dolor sit amet.

@@

>>>>

csl               : "manuscript_files/apa.csl"
documentclass     : "apa7"
classoption       : "doc,12pt,twoside"
mainfont          : "Times New Roman"
output            :
  papaja::apa6_pdf:
    latex_engine  : "xelatex"

header-includes:
  - \geometry{a4paper,margin=25mm}
  - \setcounter{tocdepth}{2}
  - \raggedbottom
  - \usepackage{ragged2e}
  - \linespread{1.5}
  - \fancyhead{}
  - \fancyheadoffset[RO,LE]{0pt}
  - \fancyhead[RO,LE]{\thepage}
  - \fancyhead[RE,LO]{Semantic Knowledge and Unfamiliar Objects}
  - \usepackage{setspace}
  - \AtBeginEnvironment{tabular}{\doublespacing}
  - \captionsetup[table]{font={stretch=1.5}}
  - \captionsetup[figure]{font={stretch=1.5}}
  - \usepackage[all]{nowidow}
  - \usepackage[bottom]{footmisc}
  - \interfootnotelinepenalty=10000
  - \usepackage[export]{adjustbox}
---

@@

<!-- Title page -->
\thispagestyle{empty}
\begin{center}
\vspace*{10mm}
\textbf{Event-Related Potentials of the Semantically Informed}\\
\textbf{Perception of Unfamiliar Objects}\\
\vspace*{5mm}
\begin{figure}[h]
\begin{center}
\includegraphics[width=!,totalheight=!,scale=0.25]{master_thesis_files/hu_logo}
\end{center}
\end{figure}
{\setstretch{1.5}
Masterarbeit\\
an der\\
Humboldt-Universität zu Berlin\\
zur Erlangung des akademischen Grades \\
Master of Science (M.Sc.)\\
im Fach Psychologie\\
\vspace*{25mm}
}
\end{center}
\begin{flushleft}
{\setstretch{1.5}
\begin{tabular}{ll}
Vorgelegt von:&\textbf{Alexander Enge}\\
&geb. am 09.11.1996 in Räckelwitz\\
&Matrikelnummer 581331\\
Fachliche Betreuung:&Prof. Dr. Rasha Abdel Rahman (Humboldt-Universität zu Berlin)\\
&Prof. Dr. Franziska Süß (Fachhochschule des Mittelstands)\\
&\\
Berlin, den 29.01.2021&\\
\end{tabular}
}
\end{flushleft}

@@

I would like to thank ... (tbc)

@@

<!-- References -->
\raggedright
\setlength{\cslhangindent}{0.5in}
<div id="refs"></div>
\justify

<!-- Appendix -->
\newpage

```{r appendix, child = "appendix.Rmd"}
```

<!-- Declaration of authorship -->
\newpage
\setlength{\parindent}{0.5in}

# Declaration of Authorship {.unnumbered}

I hereby declare that the present thesis has not been submitted as a part of any other examination procedure and has been independently written. All passages, including those from the internet, which were used directly or in modified form, especially those sources using text, graphs, charts or pictures, are indicated as such. I realize that an infringement of these principles which would amount to either an attempt of deception or deceit will lead to the institution of proceedings against myself.

\vspace*{20mm}

\noindent
Alexander Enge\newline
Berlin, 29.01.2021
